### 2019-01-17 Sections/costs_and_attributes_in_quantum_networks.tex
save

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\captionspacefig \caption{A sequence of events \mbox{$X\to Y\to Z$}. The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).}\label{fig:data_proc_ineq}	
\end{figure}

From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their \comment{classical information of the channel} is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B).
\end{align}
% \comment{Previously this was `classical mutual information'. Is that right? Isn't this actually the `accessible information'?}

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. Therefore we can optimise the mutual information of a particular channel, which leads to the following definiton:

The \comment{\textit{classical mutual information}}\index{Classical channel capacity} of quantum channel $\mathcal{E}$ is defined as,
\begin{align}
I(\mathcal{E}) = \max_{p(x)} I(X;Y),
\end{align}
where the we optimize input state density $p(x)$.
The intuitive interpretation is that this is the maximum mutual information between input and output states that can be achieved across the channel. This effectively places a physical upper bound on the achievable bitrate or bandwidth of the channel. For a noisy channel, if the input contains product states (i.e. entanglement between input states is not allowed), the classical channel capacity can be expressed as,
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\hat\rho_i} S(\hat\rho) - \sum_i p_i S(\hat\rho_i) \label{eq:holevoinfo}
\end{align}
\noindent which is known as the Holevo bound\index{Holevo bound}.

@@

@@

For a more in-depth discussion of channel capacities

\comment{This is an excellent idea to have a table summarising the different channel capacity measures!! Good thinking! Perhaps also have a column describing the interpretation of the measure, in English rather than in maths.}
% A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacities}.
% \begin{widetext}
% \begin{table}[hbt]
% \begin{tabular}{ |c | c | c| c| } \hline
% Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
% Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
% % Entanglement Assisted Classical & Classical information & Quantum mutual information &Bennett-Shor-Smolin-Thapliyal formula \\
% Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
% \end{tabular}
% \caption{\label{tab:capacities} Measure of classical and quantum channel capacities.}
% \end{table}
% \end{widetext}

@@

For a more in-depth discussion of channel capacities

>>>>

\begin{figure}[!htbp]
% \includegraphics[clip=true, width=0.3\textwidth]{data_proc_ineq}
\end{figure}

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from 
% \captionspacefig \caption{A sequence of events \mbox{$X\to Y\to Z$}.
 The data processing inequality states that the mutual information from beginning to end is upper-bounded by the mutual information between neighbouring stages, as per Eq.~(\ref{eq:data_proc_ineq}).}%\label{fig:data_proc_ineq}	
which they would like to extract maximal correlations (i.e joint information). 
They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their quantum mutual information of the channel is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\rho,\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B). \label{eq:quant_mut}
\end{align}

The intuitive interpretation is that this is the maximum mutual information between input and output states that can be achieved across the channel. This effectively places a physical upper bound on the achievable bitrate or bandwidth of the channel.

@@

 For a noisy channel, if the input contains product states as well as separable measurements,, the classical capacity 
 is equal to Eq.\eqref{eq:quant_mut}, that is, the single-use and the asymptotic classical capacities are equal.

  If we also allow joint measurement (but not entanglement between input states), the classical channel capacity can be expressed as
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\hat\rho_i} S(\hat\rho) - \sum_i p_i S(\hat\rho_i) \label{eq:holevoinfo}
\end{align}
\noindent which is known as the Holevo bound\index{Holevo bound}.

However, if entangled input states are allowed in conjunction with joint measurement setting, the Holevo bound no longer holds, and the asymptotic classical 
channel capacity
\begin{align}
\chi(\mathcal{E}) < \mathcal{C(E)}.
\end{align}

It has been shown that using entangled input states in conjunction with joint measurements can increase the amount of classical information which can be transmitted over a noisy quantum channel. In this case, the 
\begin{align}
C_\text{ent} = \lim _{n-> \infty} \frac{1}{n}\chi(\mathcal{E}^{\otimes n})
\label{eq:ent_ent}
\end{align}

The last capacity in regards to classical communication over quantum channel is the \textit{entanglement-assisted classical capacity}, $\mathcal{C}_E(\mathcal{E})$. This quantity measures the classical information that can be transmitted through the channel, if Alice and Bob possess shared entanglement prior to the transmission
\begin{align}
\mathcal{C}_E(\mathcal{E}) = \max_{p_i,\rho_i} I(A:B).
\end{align}
The difference between $\mathcal{C(E)}$ and $\mathcal{C}_E(\mathcal{E}) $ is that $\mathcal{C}_E(\mathcal{E}) $ is equal to the maximised quantum mutual information (i.e. additivity holds), and is equal to the single-use version of $\mathcal{C}_E(\mathcal{E}) $. This implies that shared entanglement does not change the additivity of quantum mutual information.

% Although entanglement does not

% The single-use 
\vspace{1cm}

We now move on to discuss quantum correlations. Whilst classical correlation measures have a clear operational meaning, quantum capacities

@@

A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacities}.
\begin{widetext}
\begin{table}[hbt]
\begin{tabular}{ |c | c | c| c| } \hline
Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
Entanglement Assisted Classical & Classical information & Quantum mutual information & See Ref.~\cite{PhysRevLett.83.3081} \\
Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
\end{tabular}
\caption{\label{tab:capacities} Measure of classical and quantum channel capacities.}
\end{table}
\end{widetext}

@@
